% !TeX program = lualatex
\documentclass{simplecv}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{dirtytalk}
\usepackage{multicol}
\usepackage[backend=biber,style=authoryear,sorting=ynt]{biblatex}
\usepackage{lipsum}

\hypersetup{
    colorlinks = true,
    urlcolor   = AccentTeal
}

\addbibresource{mybiblio.bib}

\name{Roberto Olvera Hernández}
\title{BSc. Biotechonology Engineering}
\email{roberto.olvhez@gmail.com}
\location{Zapopan}{Jalisco}{MX}
\phone{+52}{33-1540-9988}
\linkedin{\href{https://www.linkedin.com/in/rob-olvhez/}{rob-olvhez}}
\github{\href{https://github.com/robolvhez}{robolvhez}}

\begin{document}
\setmainfont{XCharter} % Sans-serif. Body. Sans can also be set as main font. Good options include: {XCharter, Heuristica, QTBasker}
\setsansfont{Inter} % Sans. Titles. Good options include: {Inter, Roboto, Cabin}
\nocite{*}
% L = Añadir localizacion; vacio = no incluir
\makecvheader{}
\thispagestyle{firstpage}

% ------------
% PROFFESIONAL PROFILE
% ------------
{\small\sffamily\setlength{\parskip}{6pt}%

}\vspace{0.75em}

% ------------
% EDUCATION
% ------------
\vspace{0.5em}
\cvsection{\education Education}
    \cvevent{B.Sc. in Biotechnology Engineering} % Carrera/posgrado/puesto
    {Instituto Tecnológico y de Estudios Superiores de Occidente (ITESO)} % Institución/empresa
    {} % Lugar
    {2018} % Inicio
    {ongoing} % Fin
    {
        \textbf{Bachelor thesis:} Genome-Wide Association Study (GWAS) for the identification of genes related to hydrotropic response in native maize (\textit{Zea mays} L.) from Mexico.
    } % Texto
    
\cvsubsection{Research experiences}

    \cvevent{GWAS for the characterization of native maize from Mexico}
        {Biotechnology Institute, National Autonomous University of Mexico (IBt -- UNAM)}
        {}
        {2023}
        {2023}
        {%
            \vspace{-11pt}
            \begin{itemize}[leftmargin=*]
            \setlength{\itemsep}{0cm}
              \item Statistical analysis in the phenotypic response of maize to drought.
              \item Data wrangling of genomic databases with R.
              \item Genome-Wide Association Analysis (GWAS) using tools such as GAPIT and TASSEL.
              \item Ancestry Analysis with ADMIXTURE (Linux Shell).
              \item NGS DArTseq sequencing protocol.
            \end{itemize}
        }

    \cvevent{Project Leader - International Competition}
    {iGEM Design League 2022 (Latin America)}
    {}
    {2021}
    {2022}
    {%
        \vspace{-11pt}
        \begin{itemize}[leftmargin=*]
        \setlength{\itemsep}{0cm}
          \item Awarded Silver Medal and Best Project Presentation.
          \item Project at the Latin American level.
          \item Interviews with farmers and entrepreneurs for market strategies.
          \item Training of the technical team in Synthetic Biology.
        \end{itemize}
    }

    % \cvevent{Participant - Worldwide Competition (iGEM 2019)}
    % {iGEM 2019 (Boston, USA)}
    % {}
    % {2019}
    % {2020}
    % {%
    %     \vspace{-11pt}
    %     \begin{itemize}[leftmargin=*]
    %     \setlength{\itemsep}{0cm}
    %       \item Interviews for market strategies and project validation.
    %       \item Analysis of government databases for wastewater treatment plants.
    %     \end{itemize}
    % }

% ------------
% EXPERIENCE
% ------------
\cvsection{\job Professional \& Academic Experience}

    %% Income Analyst - TOKA Internacional
    \cvevent{Income Analyst}
    {TOKA Internacional}
    {}
    {2024}
    {ongoing}
    {
     \vspace{-11pt}
     \begin{itemize}[leftmargin=*]
     \setlength{\itemsep}{0cm}
         \item Income monitoring and diagnosis within the payment cards market.
         \item Development of SQL/R scripts for massive data analysis.
         \item Generation and updating Power BI productive dashboards.
         \item Mapping and standardization of management processes such as billing.
     \end{itemize}
    }

    %% Process and Automation Engineer %%
    %\cvevent{Process and Automation Engineer}
    %{GDL Development}
    %{}
    %{2023}
    %{2024}
    %{
    %    \textbf{Achievements:}
    %    \begin{itemize}[leftmargin=*]
    %    \setlength{\itemsep}{0cm}
    %        \item Automation of historical inventory reports using R and SQL scripts via ODBC/MySQL connections, eliminating the need to generate multiple Excel files and backing up accessible information in an established database.
    %        \item Automation of annual inventory analysis. Reduced from 3 days to 1 day with the implementation of an R script.
    %        \item Optimized piece labeling productivity for concession by 120\%, freeing up 5 hours for shipment preparation and reducing the need for temporary staff.
    %    \end{itemize}
    %
    %    \textbf{Activities:}
    %    \begin{itemize}[leftmargin=*]
    %    \setlength{\itemsep}{0cm}
    %        \item Mapping activities in all company departments.
    %        \item Analysis of indicators for the operations area.
    %        \item Planning the purchase of supplies for the web department.
    %        \item Creating visual guides for collaborators in operations.
    %    \end{itemize}
    %}

    %% Animal Health Diagnostics Trainee %%
    \cvevent{Animal Health Diagnostics Trainee}
        {Boehringer Ingelheim --- Vetmedica}
        {}
        {2021}
        {2022}
        {%
            \vspace{-11pt}
            \begin{itemize}[leftmargin=*]
            \setlength{\itemsep}{0cm}
                \item Next Generation Sequencing (NGS) protocols for viral surveillance in poultry and swine.
                \item Implementation of Power BI in the marketing team.
                \item Management of relational databases with SQL.
                \item Automation of document reading using AI workflows.
                \item Execution of serological tests (ELISA) and molecular biology tests (RFLP and qRT-PCR).
                \item Constant contact with clients.
                \item Supply of reagents and materials in the serology lab.
            \end{itemize}
        }


    
% ------------
% HABILIDADES
% ------------
\newpage
\setlength\columnsep{0.33in}
\begin{multicols}{2}
\cvsection{\large\lang Languages}
\vspace{-8pt}
\textbf{Spanish (native)}\\
    \cvskill{Writing}{5}
    \cvskill{Reading}{5}
    \cvskill{Conversation}{5}

\medskip

\textbf{German}\\
    \cvskill{Writing}{1}
    \cvskill{Reading}{1}
    \cvskill{Conversation}{1}

\bigskip

\cvsection{\large\courses Complementary education} % Cursos, talleres y certificaciones.
\vspace{-8pt}
{\small
  \begin{itemize}[leftmargin=*]
  \setlength{\itemsep}{6pt}
    % \item \textbf{Workshop: \say{Deep Dive into Network Protocols}}\\January 2024 (8 hours) at \textit{Fireship}.
    \item \textbf{Course: \say{Bioinformatic Tools for High-Throughput Sequencing}}\\July 2023 (61 hours) at \textit{IBt - UNAM (USMBB)}. Teacher Assistant in the "Programming with R" workshop.
    \item \textbf{Complementary coursework: \say{Production planning}}\\January - May 2023 at \textit{ITESO}.
    \item \textbf{Complementary coursework: \say{Information design}}\\January - May 2023 at \textit{ITESO}.
    \item \textbf{Complementary coursework:  \say{Machine Learning Methods (Python)}}\\January - May 2022 at \textit{ITESO}
    \item \textbf{Complementary coursework: \say{PMI's Project Management}}\\August - December 2021 at \textit{ITESO}.
    \item \textbf{Course: "Synthetic Biology and Genetic Circuits 101"}\\July 2021 (28 hours) at \textit{Scintia}.
    \item \textbf{Workshop: "Malice Analysis for your project"}\\May 2021 (12 hours) at \textit{Engineering Biology Research Consortium (EBRC)}.
    \item \textbf{Course: \say{Agile Process, Project, and Program Controls}}\\February 2021 (28 hours), online course from \textit{HarvardX}.
    \item \textbf{Data Science: R Basics}\\August 2020 (60 hours), online course from \textit{HarvardX}.
  \end{itemize}
}

\bigskip

\cvsection{\large\hardskill Hard skills}
\vspace{-6pt}
\textbf{Software \& Tools}\\
    % \cvskill{Linux (Desktop)}{5}
    \cvskill{Archlinux (daily-driver)}{5}
    \cvskill{CentOS (server-driver)}{4}
    \cvskill{Git}{4}
    % \cvskill{Vim/NeoVim}{4}
    \cvskill{PowerBI}{4}
    \cvskill{Tableau}{4}
    \cvskill{Adobe Suite}{3}
    % \cvskill{MBA3}{3}
    % \cvskill{SAP B1}{2}
    \cvskill{Amazon AWS}{1}
    \cvskill{Microsoft Azure}{1}

\medskip

\textbf{Programming Languages}\\
    \cvskill{R}{5}
    \cvskill{BASH}{5}
    \cvskill{SQL}{4}
    \cvskill{Python}{3}
    \cvskill{MATLAB}{3}
    \cvskill{VBA}{2}

\bigskip

\cvsection{\large\group Softskills} % Cursos, talleres y certificaciones.

\cvtag{Collaborative work}
\cvtag{Social skills}
\cvtag{Effective communication}
\cvtag{Multilingual}
\cvtag{Human/Social Oriented}
\cvtag{Multidisciplinary teams}
\cvtag{Leadership}
\cvtag{Management}
\cvtag{Design (UI) and creativity}
\cvtag{Self-Thought Drive}


% \cvsection{\publications Publicaciones}
% \defbibnote{mynote}{$^*$ Indica contribuciones iguales;\\$^\dagger$ Indica investigador(a) principal; y\\ \textbf{bold} Indica compañeros(as) de laboratorio.}

% \cvsubsection{Publicados (peer-reviewed)}

% \begin{spacing}{1.25}
%     \printbibliography[heading=none,keyword=peerreviewed,prenote=mynote]
% \end{spacing}

% \cvsubsection{En revisión (pre-prints)}

% \begin{spacing}{1.25}
%     \printbibliography[heading=none]
% \end{spacing}
\end{multicols}
\end{document}
